### 2018-11-07 inst/table_tennis_serve.Rmd
more work on interpreting the MLE

This is easily analysed with the ```hyper2``` package.

@@

So H is the likelihood function for three players and a serve.
We now find the unconstrained MLE:

@@

>>>>

(note that A does not play C).  This dataset is easily analysed with
the ```hyper2``` package.

@@

So H is the likelihood function for three players and a serve.

# Results 
We now find the unconstrained MLE:

@@

Further, note that our estimated strengths as obtained by MLE allow us
to assess what might happen when A plays C (which was not observed).
If A serves, we would have $A+S:C\simeq 0.24+0.45:0.16\equiv 69:16$,
or A wins with probability of about $0.81$.  If C serves we have
$A:C+S\simeq 0.24:0.16+0.45\equiv 24:61$, so A wins with a probability
of about $0.28$.
